A pipeline to analyse time-course gene expression data

### 2020-06-05 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

The manuscript was last compile on 2020-04-29 10:12:35.

\#\textless{}U+00A0\textgreater{}TODO list

\begin{itemize}
\tightlist
\item
  Make clear that it applies to RNASeq and how to call the different functions
  to RNASeq
\item
  Check that clustering can deal with count data.
\end{itemize}

\emph{EAP}: What is your plan for the installation instructions Nelle? Shouldn't it be moved where we introduce the package, and give instructions about how to install it there.

@@

{\centering \includegraphics[width=4.81in]{images/fig1_schemas}

@@

@@

\hypertarget{package-versions}{%
\subsection{Package versions}\label{package-versions}}

The following packages are needed for this workflow.

To install \texttt{moanin} directly from GitHub, use the devtools' \texttt{install\_github}
function:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(devtools)}
\KeywordTok{install_github}\NormalTok{(}\StringTok{"NelleV/moanin"}\NormalTok{)}

\KeywordTok{library}\NormalTok{(moanin)}
\end{Highlighting}
\end{Shaded}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-8-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/pca_plots-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/correlation_plot-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-14-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-15-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-25-1} \end{center}

@@

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-30-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-35-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-35-2} \end{center}

@@

@@

## [65] rlang_0.4.5             pkgconfig_2.0.2        

>>>>

The manuscript was last compile on 2020-06-05 16:11:32.

\hypertarget{todo-list}{%
\section{TODO list}\label{todo-list}}

\begin{itemize}
\tightlist
\item
  Make clear that it applies to RNASeq and how to call the different functions
  to RNASeq
\item
  Check that clustering can deal with count data.
\item
  Update Nelle's affiliation!
\end{itemize}

@@

{\centering \includegraphics[width=11.53in]{images/fig1_schemas}

@@

\hypertarget{installation-and-setup}{%
\subsection{Installation and setup}\label{installation-and-setup}}

\texttt{moanin} is available from GitHub, and can be installed using the \texttt{install\_github} function in the package \texttt{devtools}:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(devtools)}
\KeywordTok{install_github}\NormalTok{(}\StringTok{"NelleV/moanin"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(moanin)}
\end{Highlighting}
\end{Shaded}

The following additional packages are needed for this workflow:

\textbf{EAP}: Why is this list not the same as the (hidden via echo=FALSE) list at the beginning of the document? I also needed to install \texttt{BiocWorkflowTools}, \texttt{KEGGprofile} to run the .Rmd

@@

@@

{\centering \includegraphics{reports/manuscript_files/figure-latex/geneVarHist-1}

\caption{Distribution of variance}\label{fig:geneVarHist}
\end{figure}

\textbf{EAP}: Not sure why you hide the code for this plot, but not for others\ldots{}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/pcaPlots-1} \end{center}

@@

{\centering \includegraphics{reports/manuscript_files/figure-latex/correlationPlot-1}

\caption{Cross-correlation of the samples}\label{fig:correlationPlot}
\end{figure}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-13-1} \end{center}

@@

{\centering \includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-14-1}

\caption{Distribution of DE genes per condition}\label{fig:unnamed-chunk-14}
\end{figure}

@@

@@

{\centering \includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-25-1}

\caption{Confusion matrix between the two sets of labels}\label{fig:unnamed-chunk-25}
\end{figure}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-29-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-34-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-34-2} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-36-1} \end{center}

@@

## [65] rlang_0.4.6             pkgconfig_2.0.2        
